Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-06 thesis/paper.tex
Table..... again

%
\usepackage{multirow}

@@

\begin{table}
       \centering
       \begin{tabular}[ht]{|c|c|c|c|c|}

              \hline

@@

                                   & \textbf{P}                & \textbf{A}                & \textbf{P}                & \textbf{A}         \\ \hline    
              Example Code         & U                         & R\textsubscript{ef}       & R\textsubscript{ef}       & U                  \\ \hline
              Documentation        & U                         & U                         & R\textsubscript{ef}       & R\textsubscript{ef} \\ \hline
              Interfaces           & G                         & P                         & P                         & G                  \\ \hline
              Error Handling       & P                         & P                         & G                         & G                  \\ \hline
              3rd Party            & A                         & A                         & N/A                       & N/A                \\ \hline
              axaudio              & E                         & E                         & N/A                       & N/A                \\ \hline
              axptz                & E                         & E                         & N/A                       & N/A                \\ \hline
              axstorage            & E                         & E                         & N/A                       & N/A                \\ \hline
              axserialport         & E                         & E                         & N/A                       & N/A                \\ \hline
              axevent              & E                         & E                         & G                         & G                  \\ \hline
              axhttp               & E                         & E                         & G                         & G                  \\ \hline
              ax\_parameter        & E                         & E                         & G                         & G                  \\ \hline
              Burst Mode           & R\textsubscript{ed}       & R\textsubscript{ed} &     N/A                         & N/A                \\ \hline

>>>>

%
\usepackage{array}
\usepackage{multirow}
\usepackage{makecell}

@@

  %\begin{tabular}{!{\vrule width 2pt}c|c|c!{\vrule width 2pt}c|c|c%

\begin{table}
       \centering
       \begin{tabular}[ht]{|c !{\vrule width 1.5pt} c|c|c|c|} 
              \hline

@@

                                   & \textbf{P}                & \textbf{A}                & \textbf{P}                & \textbf{A}         \\ \Xhline{2\arrayrulewidth}
              Example Code         & U                         & R\textsubscript{ef}       & R\textsubscript{ef}       & U                  \\ \hline
              Documentation        & U                         & U                         & R\textsubscript{ef}       & R\textsubscript{ef} \\ \hline
              Interfaces           & G                         & P                         & P                         & G                  \\ \hline
              Error Handling       & P                         & P                         & G                         & G                  \\ \hline
              3rd Party            & A                         & A                         & N/A                       & N/A                \\ \hline
              axaudio              & E                         & E                         & N/A                       & N/A                \\ \hline
              axptz                & E                         & E                         & N/A                       & N/A                \\ \hline
              axstorage            & E                         & E                         & N/A                       & N/A                \\ \hline
              axserialport         & E                         & E                         & N/A                       & N/A                \\ \hline
              axevent              & E                         & E                         & G                         & G                  \\ \hline
              axhttp               & E                         & E                         & G                         & G                  \\ \hline
              ax\_parameter        & E                         & E                         & G                         & G                  \\ \hline
              Burst Mode           & R\textsubscript{ed}       & R\textsubscript{ed} &     N/A                         & N/A                \\ \hline
